Manuscript_Github_Pchabaudi_boilerplate

### 2022-07-30 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_TPMheatmaps.Rmd
Order heatmap df by mean TPM because Complex Heatmaps will split by sub-fams itself

```{r}
#Ordering that a more understandable order

combined_data_ordered <- tibble(Geneid = names(apply(combined_data_pir, 1, mean)),
                                means = apply(combined_data_pir, 1, mean),
                                subfam = factor(
                                  ifelse(rownames(combined_data_pir) %in% cir_id,
                                         cir_info$subfam[match(rownames(combined_data_pir), 
                                                               cir_info$Geneid)],
                                         'ref')
                                )) %>% 
  mutate(subfam =
           forcats::fct_shift(
             relevel(
               as.factor(subfam),
               ref = 'ref')
           )
  ) %>% 
  # filter(means > 1) %>% 
  arrange(subfam, 
          desc(means)) %>% 
  .$Geneid

#Order the heatmap data by the order defined above (Subfam, then mean expression).
combined_data_pir_ht <- combined_data_pir[
  order(
    match(rownames(combined_data_pir),
          combined_data_ordered),
    na.last = NA #Remove NAs
  ),
]

#Change the colnames to the times
colnames(combined_data_pir_ht) <- str_extract(colnames(combined_data_pir_ht),
                                              pattern = '.{3}_([[:digit:]]{2}h|sch.culture)')

#Order by time point
combined_data_pir_ht <- combined_data_pir_ht[,order(colnames(combined_data_pir_ht)),
                                             drop = FALSE] 
```

```{r}
#Add a column for the subfam (ref for the reference genes)
combined_data_pir_ht$subfam <- ifelse(rownames(combined_data_pir_ht) %in% cir_id,
                                      cir_info$subfam_num[match(rownames(combined_data_pir_ht), 
                                                            cir_info$Geneid)],
                                      'ref')

>>>>

```{r heatmap_df}
combined_data_pir_ht <- combined_data_pir
#Change the colnames to the times
colnames(combined_data_pir_ht) <- str_extract(colnames(combined_data_pir_ht),
                                              pattern = '.{3}_([[:digit:]]{2}h|sch.culture)')

#Order by time point
combined_data_pir_ht <- combined_data_pir_ht[,order(colnames(combined_data_pir_ht)),
                                             drop = FALSE]

#Add mean column for ordering
combined_data_pir_ht$mean_tpm <- apply(combined_data_pir_ht, 1, mean)

combined_data_pir_ht <- arrange(combined_data_pir_ht, desc(mean_tpm))

#Add a column for the subfam (ref for the reference genes)
combined_data_pir_ht$subfam <- ifelse(rownames(combined_data_pir_ht) %in% cir_id,
                                      cir_info$subfam_num[match(rownames(combined_data_pir_ht), 
                                                            cir_info$Geneid)],
                                      'ref')
